A word-sense representation for documents based on information value and word sense disambiguation

### 2014-03-19 paper/refactor.tex

\section{Conclussion \& Future work}
The original scope of this investigation was the definition of a measure of distance between the works of a whole year and a concept; so we could measure whether the literary production of Lenin in some year was close to ``revolution'', ``theory'', etc.  With this purpose, we defined the \textbf{top senses} of a text, and measured the distance between them and other senses in a topological way.

>>>>

\section{Conclussion \& Future work}
The original scope of this investigation was the definit'ion of a measure of distance between the works of a whole year and a concept; so we could measure whether the literary production of Lenin in some year was close to ``revolution'', ``theory'', etc.
